The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-02-10 paper/ms.tex
Fixed typo in new figure.
Moved figure around a bit.
Tweaked ccf figure and added imaging data figure.

@@

We list the companion detections in Table \ref{tab:companions}, and report the estimate of the companion temperature, $v\sin{i}$, and metallicity derived from the model parameters which produce the largest CCF peak. The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value. We show the detection CCFs and a plot of peak CCF height as a function of model temperature in Figure \ref{fig:ccf}. Similar figures for all companions are available in the supplementary files.

\begin{figure}
\includegraphics[width=\pagewidth]{HIP_109139.pdf}
\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra. The detection at two dates shows significant velocity variation, indicating orbital motion with a short period. \emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature. The maxima of the curves indicate the temperature of the companion.}
\label{fig:ccf}
\end{figure}

Most of the detected companions have follow-up spectra to confirm the existence of the companion. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion. In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}.

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{HIP_109139.pdf}
\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra. The detection at two dates shows significant velocity variation, indicating orbital motion with a short period. \emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature. The maxima of the curves indicate the temperature of the companion.}
\label{fig:ccf}
\end{figure*}

@@

We list the companion detections in Table \ref{tab:companions}, and report the estimate of the companion temperature, $v\sin{i}$, and metallicity derived from the model parameters which produce the largest CCF peak. The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value. We show the detection CCFs and a plot of peak CCF height as a function of model temperature for HIP 109139 in Figure \ref{fig:ccf}. Similar figures for all companions are available in the supplementary files.

Most of the detected companions have follow-up spectra to confirm the existence of the companion. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion (See Figure \ref{fig:ccf}). In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.

\begin{figure}
\includegraphics[width=\columnwidth]{Imaging_Data.pdf}
\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data.}
\label{fig:images}
\end{figure}
